---
title       : Overview of the Basic Car Research Application (BCRA version 0.1)
subtitle    : A Project for the Coursera-JHU Data Products Course
author      : Jon Breece
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The Basic Car Research Application

* Buying a car is confusing
* This application allows buyers to compare vehicles quickly
* https://breecejon.shinyapps.io/Basic_Car_Research_Application/ 
* This application will help you compare cars in the mtcars dataset. Use the drop-downs to pick variables for Plot 1.  Use the slider to select the number of bins for Plots 2 and 3. Lastly, use the numeric input box to select how many cars that would like to see in the table at the bottom.

---

## The mtcars dataset

The application relies on the mtcars dataset

```{r eval=TRUE, echo=TRUE}
head(mtcars)
nrow(mtcars)
```

---

## User controls
#### The user has to make four choices:
1. Variable 1: From the mtcars dataset (e.g., mpg, cyl, hp, etc.)
2. Variable 2: From the mtcars dataset (e.g., mpg, cyl, hp, etc.)
3. Number of bins for histograms -- using a slider
4. Number of cars to show in table -- using a numeric input


---

## Outputs
Outputs include three graphs, such as Plot 1:

```{r eval=TRUE, echo=FALSE}
ggplot(mtcars, aes(mpg,hp)) + geom_label(label=rownames(mtcars)) + geom_smooth(method = "lm", se = FALSE, color = "blue", formula = y ~ x)
```

---

## Thank you

* Thank you for your time.  
* Now check out the app: https://breecejon.shinyapps.io/Basic_Car_Research_Application/
```{r eval=TRUE, echo=FALSE}
ggplot(mtcars, aes(mpg)) + geom_histogram(bins = 10)
```
